A Linear Solution of the Linearity Challenge

### 2025-12-19 paper/main.tex
revised congruence
restored examples
cleanup

\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsthm}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{stmaryrd}
\usepackage{mathpartir}
\usepackage{agda}
\usepackage{xspace}
\usepackage{upgreek}
\usepackage{cleveref}
\usepackage{newunicodechar}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%%%%
\input{macros}

@@

\title{A Splitting Solution of the Linearity Challenge}

@@

\author[2]{\fnm{Claudia} \sur{Raffaelli}}\email{xxx@yyy.zzz}
\equalcont{These authors contributed equally to this work.}

\affil*[1]{\orgdiv{Department of Computer Science and Engineering}, \orgname{Università di Bologna}, \orgaddress{\street{Mura Anteo Zamboni 7}, \city{Bologna}, \postcode{40138}, \state{BO}, \country{Italy}}}

@@

\keywords{keyword1, Keyword2, Keyword3, Keyword4}

@@

\input{introduction}
\input{calculus}
\input{agda}
% \input{Examples}
\input{related}
\input{conclusion}

>>>>

\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{stmaryrd}
\usepackage{mathpartir}
\usepackage{agda}
\usepackage{xspace}
\usepackage{upgreek}
\usepackage{cleveref}
\usepackage{newunicodechar}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\input{macros}

@@

\title{A Linear Solution of the Linearity Challenge}

@@

\author[2]{\fnm{Claudia} \sur{Raffaelli}}\email{claudia.raffaelli@studenti.unicam.it}

\affil[1]{\orgdiv{Department of Computer Science and Engineering}, \orgname{Università di Bologna}, \orgaddress{\street{Mura Anteo Zamboni 7}, \city{Bologna}, \postcode{40126}, \state{BO}, \country{Italy}}}

@@

\keywords{session types, linear logic, deadlock freedom, Agda}

@@

\input{introduction}
\input{calculus}
\input{agda}
\input{related}
\input{conclusion}
